Holomorphic field theories and higher algebra

### 2022-11-10 draft.tex
tried to improve end of SD section

A major endeavor in theoretical physics is to develop a deep and effective understanding of theories like quantum chromodynamics (QCD), which governs the behavior of quarks and gluons.
One natural approach is to study theories that are close cousins but that are easier to analyze,
and a notable way is to look for theories with the same ingredients but with larger groups of symmetries.
Supersymmetric Yang--Mills theories are quite appealing in this regard,
and there have been remarkable successes in this direction.
A well-known high point is the work of Seiberg and Witten on 4-dimensional $\cN =2$ supersymmetric Yang--Mills theory,
where they explained how confinement could be realized by a version of the Mandelstam-'t Hooft mechanism (i.e., a kind of electromagnetic duality identifies confinement with a Meissner effect).
Their work offered powerful new tools that opened up much subsequent progress,
and even impacted mathematics through the Seiberg-Witten equations (which is related to the topologically twisted versions of $\cN=2$ theory).

@@

The twisted vector multiplet defines a field theory on any complex surface $X$ often called {\em holomorphic BF theory}. 
It will be convenient for us to assume that $X$ is equipped with a holomorphic volume form that we denote by $\Omega_X$. 
A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of the adjoint bundle ${\mathrm ad}(\cP) \to X$.
The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.
\brian{got rid of the term `shifted' section. Also, to write theory like this we use a CY structure, which I've now fixed.e}

@@

Since $W$ is $G_\CC$-invariant, the critical locus has a residual Hamiltonian $G_\CC$-action. 
There is a version of Hamiltonian reduction for odd symplectic manifolds \cite{Pavel, Kevin, who else},
which we denote by ${\rm Crit}(W) \Sslash G_\CC$. 
\owen{I'm not sure we even need this.} \brian{Probably if we want to cite a model for it, I think its fine to list the references here though.}
%As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$. 
The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
\[
{\rm Map}(X , {\rm Crit}^d(W) \Sslash G_\CC), 
\]
which comes equipped with an odd symplectic structure. 
\owen{Should there also be a factor involving the $B$-fields of the BF gauge theory?}
\brian{That's already in this hamiltonian reduction. 
If $V$ is $(-1)$ shifted symplectic then I think the tangent space of $V \Sslash G$ should be
\beqn
\lie{g}[1] \oplus V \oplus \lie{g}^*[-2] .
\eeqn
Since we're forgetting to $\ZZ/2$ this is just $\Pi \lie{g} \oplus (V \oplus \lie{g})$.
}

@@

The action functional is
\[
S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.
\owen{Should we make explicit how we're using the evaluation pairing on fields and their ``conjugates''? Or do we explain that in our review of BF theories?}
\brian{BTW, I think you've now switched from lower case $r,q$ for antiquarks to $R^\dag, Q^\dag$, is that right?
}
%We will denote this theory by $\cT(N,F)$.
\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
\end{dfn}

@@

\begin{dfn}
A holomorphic QCD theory {\em with mesons}
%, denoted $\cT(N,F, V_M, W)$, 
is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
\[
\mu \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad \nu \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
\]
The action functional is
\[
S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; W(Q, Q^\dag, \mu) .
\] 
Notice that to write down the superpotential term we are utilizing the holomorphic volume form $\Omega_X = \d^2 z$. 
\end{dfn}

Note that the fields $\mu$ are ``uncharged,'' i.e., $SL(N)$ acts trivially on $V_M$.
The only coupling that the meson $\mu$ has to the other fields is through the superpotential~$W$.

@@

Our long-term goal is to show that two special cases of holomorphic QCD are {\em dual}.
The notion of duality can refer to several kinds of relationships,
but loosely speaking it means that some aspects of the two theories are equivalent under correspondence.
We will postpone saying anything precise till we have some terminology in place.

@@

The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors, {\em without} mesons.
We denote it by~$\cT_{\sfE}(F, N)$.
We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.

The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
(and $\check{L}$ for the partner field to $\check{M}$).
We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q}),$$
where we compose the linear maps before tracing over~$V_{\check{N}}$.
\owen{Please double-check that formula.}
\end{dfn}

@@

\begin{rmk}
Our discussion here is ahistorical.
Witten initiated this vein of research for topological twists \cite{},
and Costello pushed it for holomorphic twists, particularly in the setting of holography \cite{}.
Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
\owen{Add a remark (?) about Kevin and Si's work on twisted holography and other related directions.}
\end{rmk}

@@

It is fruitful, and standard in physics, to identify the simplest solutions to the equations of motion for a theory.
Here that means a solution that is translation-invariant on $\CC^2$ (i.e., a constant solution),
and we call such a solution a {\em classical vacuum}.
Thus each theory has an associated {\em moduli space of classical vacua},
which we describe in the next subsection.
Each vacuum determines a perturbative field theory that one could try to quantize,
and we have shown the following.
(Many arguments are close cousins of~\cite{EGW}, where we quantize every twist over a moduli of vacua of the $\cN=4$ supersymmetric Yang--Mills theory.)

@@

Many stacks of interest to geometers and representation theorists appear naturally from holomorphic field theories.
For example, the holomorphic $\sigma$-model from $\CC^d$ into a target complex manifold $X$ has
\[
\cM_{\rm vac} \cong T^*[1-d]X.
\]
(If we consider the underlying underived stack, it is just $X$, unless $d = 1$.)
For supersymmetric gauge theories, the moduli stack of the holomorphic twist has the form
\[
\cM_{\rm vac} \cong [V/G]
\]
where $V$ is a (graded) $G$-representation and $[V/G]$ denotes the quotient stack.
The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
the quotient by $G$ arises from the gauge transformation.
For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has
\[
\cM_{\rm vac} \cong \fg^*/G,
\]
the coadjoint quotient stack of the group.
(We are working in a $\ZZ/2$-graded world here.)
Using the invariant pairing on $\fg$ we can further identify this with the adjoint quotient stack~$\fg / G$. 
For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
\[
\cM_{\rm vac} \cong [X/G]
\]
where $X$ is a derived stack with a $G$-action and $[X/G]$ denotes the quotient stack.

@@

It is familiar to geometers that this affinization forgets interesting information about the stack because an invariant function must be constant on the closure of any orbit.
Thus, the canonical map
\[
[V/G] \to V\Sslash G
\]
often collapses orbits together.
An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $[\gl_N/ GL_N]$, whose affinization is
\[
\gl_N \Sslash GL_N \cong \CC^N,
\]
by the Chevalley restriction theorem $\cO(\gl_N)^{\GL_N} \cong \cO(\frak{h})^{S_N}$ where $\frak{h}$ denotes the maximal torus.
(The rightmost algebra is symmetric polynomials.)
The canonical map here records the characteristic polynomial of a matrix and hence only knows its generalized eigenvalues and not its Jordan decomposition.
In other words, the canonical map collapses together Jordan blocks with the same diagonal entries.
For this reason, it loses details about the classical vacua remembered by the stack quotient.

\begin{rmk}
The physicists' focus on the moduli space is not unreasonable:
one must make measurements --- i.e., evaluate functions --- to identify the state of a physical system.
The moduli space captures what can be seen by measurements (notably here, the ``vacuum expectation values'' of different vacua).
In other words, the possible classical states --- viewed as suitable linear functionals on the algebra of observables --- are parametrized by the underlying affine scheme of the derived moduli stack.
On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion,
and hence records much more about the classical theory; 
the space cannot distinguish between some vacua because it collapses orbits.
Moreover, the stack encodes much more data about the theory near each vacuum.
For instance, it remembers ``enhanced symmetries'' (such as the residual gauge fields) at each vacuum.
\end{rmk}

For the holomorphic QCD theory with $F$ flavors and $N$ colors (without mesons), 
the moduli stack of classical vacua is 
\[
\cM_{\rm vac}(F,N) \cong T^*[1] \left(V_Q \oplus V_Q^*/SL(N)\right).
\]
By contrast the moduli space $M_{\rm vac}$ is a variety already well-studied in classical algebraic geometry.
Before we jump to the full space, let's examine a simpler case involving just the quarks.
A vacuum for the quark field is an element of $V_Q = \Hom(\CC^F, \CC^N)$,
and it is a classic result of invariant theory that
\[
\Hom(\CC^F, \CC^N)\Sslash SL(N) \cong \widehat{{\rm Gr}(F, N)} \subset \Lambda^N \CC^F
\]
where ${\rm Gr}(F, N)$ denotes the Grassmannian of $N$-planes in $\CC^F$ and the hat indicates we take the affine cone with respect to this standard Pl\"ucker embedding.
For the full problem, we have both quarks and antiquarks, so
\begin{align*}
M_{\rm vac}(F,N) 
&\cong V_Q \oplus V_Q^*\Sslash SL(N) \\
&= \Hom(\CC^F, \CC^N) \oplus \Hom(\CC^N, \CC^F)\Sslash SL(N),
\end{align*}
whose ring of functions is also computed by the fundamental theorems of invariant theory.
Those theorems tell us that the GIT quotient is a closed conical subvariety
\[
M_{\rm vac}(F,N)  \hookrightarrow \Lambda^N \CC^F \times \Lambda^N (\CC^F)^* \times \End(\CC^F)
\]
where a pair of matrices $(X,Y) \in \Hom(\CC^F, \CC^N) \times \Hom(\CC^N, \CC^F)$ goes to $(\Lambda^N X, \Lambda^N Y, YX)$, with $\Lambda^N X$ denoting the wedge product of the rows of $X$ (and of columns for $Y$).
The image thus satisfies both sets of Pl\"ucker relations, the condition that the composite $YX$ has rank at most $N$, and some further relations, given by the Second Fundamental Theorem, such as that the pairing of $\Lambda^N X$ and $\Lambda^N Y$ can be related to $\Lambda^N (YX)$.
(See Chapter 2, Section C of \cite{Weyl}.)
In other words, we have a closed subvariety
\[
M_{\rm vac}(F,N) \hookrightarrow \widehat{{\rm Gr}(F, N)} \times \widehat{{\rm Gr}(F, N)} \times {\rm R}(F,N)
\]
with ${\rm R}(F,N) \subset \End(\CC^F)$ the matrices with rank bounded above by~$N$.
The moduli space for the magnetic theory is a bit more complicated but follows from classical invariant theory as well.

@@

\begin{prop}
There is an anomaly at the quantum level for the holomorphic flavor symmetry action for both the electric and magnetic theories,
and they agree: they are labeled by the same cocycle 
\[
\theta_\sfE = \theta_\sfM.
\] 
In particular, the local observables $\Obs_{\sfE} (0), \Obs_{\sfM} (0)$ are modules for the {\em same} $2$-dimensional higher Kac--Moody algebra $\Hat{\sl(F)}_{2,\theta}$ which is a central extension of the $S^3$-mode algebra $\sl(F) \otimes \sfA_2$.
\end{prop}

@@

A beautiful maneuver of physics is compactification, where one takes a field theory $\cT$ in $n$ dimensions and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
We have already worked with a factorization algebra version of these maneuvers: 
pushing forward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
For a holomorphic factorization algebra $\cF$, the pushforward $\rho_* \cF$ is locally constant on $\RR_{\geq 0}^2 \cong \RR^2$, and hence it encodes an $E_2$-algebra.
We now apply this result in the context of holomorphic QCD and see what Seiberg duality would mean.

@@

******** Discussion about quantization **********

On the other hand, there is an open locus where the moduli stacks are equivalent:
the semi-stable points of the moduli stacks $\cM_{\rm vac}$ \owen{fix description, as it's possibly just the stable locus or (weakly) stable locus}.
This locus determines the space $V\Sslash G$ and hence we have the isomorphism desired.
Let us try to unravel what this equivalence means for the field theories, both classical and quantum.

Consider any semistable point $x$.
We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the tangent space $T_x \cM_{\rm vac}$ \owen{Elaborate: more accurately, it's into the formal neighborhood}. 
Hence the isomorphism of moduli spaces assures us there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$
because there is an explicit identification of the tangent space to the corresponding point in the moduli space of the dual theory.
Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
Hence on the semistable locus of $\cM_{\rm vac}$, we can guarantee an equivalence of quantizations.

This identification breaks down on the unstable locus, raising the following question:
\begin{quote}
At the quantum level, what happens on the unstable locus? 
\end{quote}
Each unstable point labels a theory with a nonabelian gauge group (``enhanced gauge symmetry''),
and hence its quantization is more involved that at a semistable point and depends nontrivially the gauge group.

In a related vein, we want to know what correspondence of quantum factorization algebras we expect from Seiberg duality. 
The mismatch between the moduli stack of classical vacua makes it seem highly unlikely that we obtain an equivalence after quantization.

We note that in the physics literature, there are a number of modifications that are explored in this setting.
For instance, there are ``instanton corrections'' that cannot be found by perturbative techniques, although they can be treated in a mathematically precise way. 
\owen{Mention others? RG flow, symmetry breaking, ...}
It is interesting to wonder how these would appear in the holomorphic setting.

\owen{Other things: affinization as polydiscs algebras}

* Explain that you get a sheaf of polydiscs algebras over the moduli stack. We can view this as presenting a ``quantization of the moduli stack'' $\cM_{vac}^{\rm q}$ There is thus an ``affinization'' of the quantum moduli stack.

\begin{conj}
There is an equivalence of affinizations of the quantum moduli stacks for Seiberg dual theories.
That is, the quantum moduli spaces are isomorphic.
\end{conj}

This process probably ``looks away'' from the unstable locus in much the way that it does at the classical level,
which provided our identification of moduli spaces of classical vacua.

>>>>

A major endeavor in theoretical physics is to develop a deep and effective understanding of theories like quantum chromodynamics (QCD), which governs the behavior of quarks and gluons.
One natural approach is to study theories that are close cousins but that are easier to analyze,
and a notable way is to look for theories with the same ingredients but with larger groups of symmetries.
Supersymmetric Yang--Mills theories are quite appealing in this regard,
and there have been remarkable successes in this direction.
A well-known high point is the work of Seiberg and Witten on 4-dimensional $\cN =2$ supersymmetric Yang--Mills theory,
where they explained how confinement could be realized by a version of the Mandelstam-'t Hooft mechanism (i.e., a kind of electromagnetic duality identifies confinement with a Meissner effect).
Their work offered powerful new tools that opened up much subsequent progress,
and even impacted mathematics through the Seiberg-Witten equations (which are related to the topologically twisted versions of $\cN=2$ theory).

@@

The twisted vector multiplet defines a field theory on any complex surface $X$ often called {\em holomorphic BF theory}. 
It will be convenient for us to assume that $X$ is equipped with a holomorphic volume form that we denote by $\Omega_X$. 
A solution encodes a holomorphic $G_\CC$-bundle $\cP \to X$ (by picking out a $\dbar$-connection on the underlying smooth bundle) and a holomorphic section of the adjoint bundle $\mathrm{ad}(\cP) \to X$.
The moduli space can be expressed as the mapping space ${\rm Map}(X, T^*[1]BG_{\CC})$, as a derived stack.
\brian{got rid of the term `shifted' section. Also, to write theory like this we use a CY structure, which I've now fixed.e}

@@

Since $W$ is $G_\CC$-invariant, the critical locus has a residual Hamiltonian $G_\CC$-action. 
There is a version of Hamiltonian reduction for odd symplectic manifolds \cite{Pavel, Kevin, who else},
which we denote by ${\rm Crit}(W) \Sslash G_\CC$. 
\owen{I'm not sure we even need this.} \brian{Probably if we want to cite a model for it, I think its fine to list the references here though.}
\owen{Part of my concern is that Hamiltonian reduction is a version of GIT, and hence it is {\em not} stacky. The stack quotient seems more appropriate to me.}
%As a dg space, the ring of functions is $\clie^\bu\big(\fg , \cO(\fg^* \oplus \Pi \T^* V) \big)$ where the differential is the Chevalley--Eilenberg differential plus $\iota_{\d W}$. 
The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
\[
{\rm Map}(X , {\rm Crit}^d(W) \Sslash G_\CC), 
\]
which comes equipped with an odd symplectic structure. 
\owen{Should there also be a factor involving the $B$-fields of the BF gauge theory?}
\brian{That's already in this hamiltonian reduction. 
If $V$ is $(-1)$ shifted symplectic then I think the tangent space of $V \Sslash G$ should be
\beqn
\lie{g}[1] \oplus V \oplus \lie{g}^*[-2] .
\eeqn
Since we're forgetting to $\ZZ/2$ this is just $\Pi \lie{g} \oplus (V \oplus \lie{g})$.
}

@@

The action functional is
\[
S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int R^\dag \,\dbar_A Q^\dag,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.}
\owen{Should we make explicit how we're using the evaluation pairing on fields and their ``conjugates''? Or do we explain that in our review of BF theories?}
%We will denote this theory by $\cT(N,F)$.
\end{dfn}

@@

\begin{dfn}
A holomorphic QCD theory {\em with mesons}
%, denoted $\cT(N,F, V_M, W)$, 
is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
\[
\mu \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad \nu \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
\]
The action functional is
\[
S_{QCDwM} = S_{QCD} + \int \nu \,\dbar \mu + \int \d^2 z \; W(Q, Q^\dag, \mu) .
\] 
Notice that to write down the superpotential term, we are utilizing the holomorphic volume form~$\Omega_X = \d^2 z$. 
\end{dfn}

Note that the fields $\mu$ are ``uncharged,'' i.e., $SL(N)$ acts trivially on $V_M$.
Hence we use $\dbar$ rather than $\dbar_A$.
The only coupling that the meson $\mu$ has to the other fields is through the superpotential~$W$.

@@

Our long-term goal is to show that two special cases of holomorphic QCD are {\em dual}.
The notion of duality can refer to several kinds of relationships,
but loosely speaking it means that some aspects of the two theories are equivalent under some correspondence.
We will postpone saying anything precise till we have some terminology in place.

@@

The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors and {\em without} mesons.
We denote it by~$\cT_{\sfE}(F, N)$.
We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.

The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
(and $\check{\nu}$ for the partner field to $\check{\mu}$).
We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q}),$$
where we compose the linear maps before tracing over~$V_{\check{N}}$.
\owen{Please double-check that formula.}
\end{dfn}

@@

\begin{rmk}
Our discussion here is ahistorical.
Witten initiated this vein of research for topological twists \cite{},
and Costello advocated it for holomorphic twists, particularly in the setting of holography \cite{}.
Eager's suggestion was a natural variation on this theme but it (seems to) involve physical ideas and methods that have not (yet) played a large role in Costello's program.
\owen{Add a remark (?) about Kevin and Si's work on twisted holography and other related directions.}
\end{rmk}

@@

It is fruitful, and standard in physics, to identify the simplest solutions to the equations of motion for a theory.
Here that means a solution that is translation-invariant on $\CC^2$ (i.e., a constant solution),
and we call such a solution a {\em classical vacuum}.
Thus each theory has an associated {\em moduli space of classical vacua},
which we describe below.
Each vacuum determines a perturbative field theory that one could try to quantize,
and we have shown the following.
(Many arguments are close cousins of~\cite{EGW}, where we quantize every twist over a moduli of vacua of the $\cN=4$ supersymmetric Yang--Mills theory.)

@@

Many stacks of interest to geometers and representation theorists appear naturally from holomorphic field theories.
For example, the holomorphic $\sigma$-model from $\CC^d$ into a target complex manifold $X$ has
\[
\cM_{\rm vac} \cong T^*[1-d]X.
\]
(If we consider the underlying underived stack, it is just $X$, unless $d = 1$.)
For supersymmetric gauge theories, the moduli stack of the holomorphic twist has the form
\[
\cM_{\rm vac} \cong [V/G]
\]
where $V$ is a (graded) $G$-representation and $[V/G]$ denotes the quotient stack.
The factor $V$ depends on the non-gauge fields (i.e., matter multiplets), which are sections of some associated vector bundle;
the quotient by $G$ arises from the gauge transformation.
For example, pure $\cN =1$ holomorphic Yang-Mills theory for group $G$ (i.e., the vector multiplet) has
\[
\cM_{\rm vac} \cong [\fg^*/G],
\]
the coadjoint quotient stack of the group.
(We are working in a $\ZZ/2$-graded world here.)
Using the invariant pairing on $\fg$ we can further identify this with the adjoint quotient stack~$[\fg / G]$. 
For general supersymmetric field theories, which involve both a $\sigma$-model and gauge fields, the holomorphic twist has a moduli stack of classical vacua of the form
\[
\cM_{\rm vac} \cong [X/G]
\]
where $X$ is a derived stack with a $G$-action and $[X/G]$ denotes the quotient stack.

@@

It is familiar to geometers that this affinization forgets interesting information about the stack because an invariant function must be constant on the closure of any orbit.
Thus, the canonical map
\[
[V/G] \to V\Sslash G
\]
often collapses orbits together.
An important example, pertinent to $\cN =1$ super Yang-Mills theory, is the adjoint quotient $[\gl_N/ GL_N]$.
Its affinization is
\[
\gl_N \Sslash GL_N \cong \CC^N
\]
by the Chevalley restriction theorem, 
which says $\cO(\gl_N)^{\GL_N} \cong \cO(\frak{h})^{S_N}$ where $\frak{h}$ denotes the maximal torus.
(The rightmost algebra is symmetric polynomials.)
The canonical map here records the characteristic polynomial of a matrix and hence only knows its generalized eigenvalues and not its Jordan decomposition.
In other words, the canonical map collapses together Jordan blocks with the same diagonal entries.
For this reason, it loses details about the classical vacua remembered by the stack quotient.

\begin{rmk}
The physicists' focus on the moduli space is not unreasonable:
one must make measurements --- i.e., evaluate functions --- to identify the state of a physical system.
The moduli space captures what can be seen by measurements (notably here, the ``vacuum expectation values'' of different vacua).
In other words, the possible classical states --- viewed as multiplicative linear functionals on the algebra of observables --- are parametrized by the underlying affine scheme of the derived moduli stack.
On the other hand, the moduli stack knows each orbit, which provides a distinct solution to the equations of motion,
and hence records much more about the classical theory; 
the space cannot distinguish between some vacua because it collapses orbits.
Moreover, the stack encodes much more data about the theory near each vacuum.
For instance, it remembers ``enhanced symmetries'' (such as the residual gauge fields) at each vacuum.
\end{rmk}

For the holomorphic QCD theory with $F$ flavors and $N$ colors (without mesons), 
the moduli stack of classical vacua is 
\[
\cM_{\rm vac}(F,N) \cong T^*[1] \left(V_Q \oplus V_Q^*/SL(N)\right).
\]
By contrast the moduli space $M_{\rm vac}$ is a variety already well-studied in classical algebraic geometry.
Before we describe the full space, let's examine a simpler case involving just the quarks.
A vacuum for the quark field is an element of $V_Q = \Hom(\CC^F, \CC^N)$,
and it is a classic result of invariant theory that
\[
\Hom(\CC^F, \CC^N)\Sslash SL(N) \cong \widehat{{\rm Gr}(F, N)} \subset \Lambda^N \CC^F
\]
where ${\rm Gr}(F, N)$ denotes the Grassmannian of $N$-planes in $\CC^F$ and the hat indicates we take the affine cone with respect to this standard Pl\"ucker embedding.
For the full problem, we have both quarks and antiquarks, so
\begin{align*}
M_{\rm vac}(F,N) 
&\cong V_Q \oplus V_Q^*\Sslash SL(N) \\
&= \Hom(\CC^F, \CC^N) \oplus \Hom(\CC^N, \CC^F)\Sslash SL(N),
\end{align*}
whose ring of functions is also computed by the fundamental theorems of invariant theory.
Those theorems tell us that the GIT quotient is a closed conical subvariety
\[
M_{\rm vac}(F,N)  \hookrightarrow \Lambda^N \CC^F \times \Lambda^N (\CC^F)^* \times \End(\CC^F)
\]
where a pair of matrices $(X,Y) \in \Hom(\CC^F, \CC^N) \times \Hom(\CC^N, \CC^F)$ goes to $(\Lambda^N X, \Lambda^N Y, YX)$, with $\Lambda^N X$ denoting the wedge product of the rows of $X$ (and of columns for $Y$).
The image thus satisfies both sets of Pl\"ucker relations, the condition that the composite $YX$ has rank at most $N$, and some further relations, given by the Second Fundamental Theorem, such as that the pairing of $\Lambda^N X$ and $\Lambda^N Y$ can be related to $\Lambda^N (YX)$.
(See Chapter 2, Section C of \cite{Weyl}.)
In other words, we have a closed subvariety
\[
M_{\rm vac}(F,N) \hookrightarrow \widehat{{\rm Gr}(F, N)} \times \widehat{{\rm Gr}(F, N)} \times {\rm R}(F,N)
\]
with ${\rm R}(F,N) \subset \End(\CC^F)$ the matrices with rank bounded above by~$N$.
The moduli space for the magnetic theory is a bit more complicated but follows from classical invariant theory as well.

@@

\begin{prop}
For both the electric and magnetic theories, there is an anomaly at the quantum level for the holomorphic flavor symmetry action.
These anaomlies agree: they are labeled by the same cocycle 
\[
\theta_\sfE = \theta_\sfM.
\] 
In particular, the local observables $\Obs_{\sfE} (0), \Obs_{\sfM} (0)$ are modules for the {\em same} $2$-dimensional higher Kac--Moody algebra $\Hat{\sl(F)}_{2,\theta}$ which is a central extension of the $S^3$-mode algebra $\sl(F) \otimes \sfA_2$.
\end{prop}

@@

A beautiful maneuver used in physics is compactification:
given a field theory $\cT$ in $n$ dimensions, one takes an $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
We have already worked with a factorization algebra version of these maneuvers: 
pushing forward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
For a holomorphic factorization algebra $\cF$, the pushforward $\rho_* \cF$ is locally constant on $\RR_{\geq 0}^2 \cong \RR^2$, and hence it encodes an $E_2$-algebra.
We now apply this result in the context of holomorphic QCD and see what Seiberg duality would mean.

@@

\subsubsection{Subtleties with vacua}

We saw that the moduli stacks of classical vacua are not equivalent, due to points with interesting stabilizers.
On the other hand, there is an open locus where the moduli stacks are equivalent:
the semi-stable points of the moduli stacks $\cM_{\rm vac}$ \owen{fix description, as it's possibly just the stable locus or (weakly) stable locus}.
This locus determines the GIT quotients and hence explains the isomorphism we saw on the moduli spaces.
Let us try to unravel what this equivalence means for the field theories, both classical and quantum.

Consider any semistable point $x$.
We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the formal neighborhood of $x$ inside the moduli stack of vacua. 
The isomorphism of moduli spaces ensures that there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$,
because there is an explicit identification of the formal neighborhood of $x$ with the formal neighborhood of $x_D$. 
Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
Hence on the semistable locus of $\cM_{\rm vac}$, we can guarantee an equivalence of quantizations.

\begin{prop}
The isomorphism between the semi-stable locus of the two moduli stacks determines an isomorphism between quantizations over those loci.
\end{prop}

This identification breaks down on the unstable locus, raising the following question:
\begin{quote}
At the quantum level, what happens on the unstable locus? 
\end{quote}
Each unstable point labels a theory with a nonabelian gauge group (``enhanced gauge symmetry''),
and hence its quantization is more involved that at a semistable point and depends nontrivially the gauge group.
The mismatch between the moduli stack of classical vacua makes it seem highly unlikely that we obtain an equivalence after quantization.

\subsubsection{A proposal}

Recall that the moduli space arises from the moduli stack by affinization.
In other words, we move from studying translation-invariant solutions (the stack) to studying ``states'' (multiplicative linear functionals on the stack of solutions).
The moduli of classical states are isomorphic.
We hope that something similar happens at the quantum level.
In other words, there is a moduli stack of quantum vacua and a moduli space of quantum vacua,
and we hope the spaces are isomorphic.
We sketch the idea as follows.

\begin{dfn}
For a holomorphic QCD theory let $\cM^q_{\rm vac}(F,N)$ denote the stack $\cM_{\rm vac}(F,N)$ equipped with a sheaf of factorization algebras on $\CC^2$.
The value at a solution $x$ is a quantization of the observables for the classical perturbative theory labeled by~$x$.
(One could focus, for simplicity, on the sheaf of polydiscs algebras.)

Let $M^q_{\rm vac}(F,N)$ denote the global sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
It is a factorization algebra on~$\CC^2$.
(Again, one could focus, for simplicity, on the polydiscs algebra.)
\end{dfn}

We view $M^q_{\rm vac}(F,N)$ as an affinization of $\cM^q_{\rm vac}(F,N)$.
Optimistically, we refine Eager's conjecture to the following.

\begin{conj}
Let $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
There is an equivalence of 2-dimensional holomorphic factorization algebras
\[
M^q_{\rm vac}(F,N)_{\sfE} \simeq M^q_{\rm vac}(F,\check{N})_{\sfM}.
\]
\end{conj}

We note that there may be many quantizations possible, but our experience in $\cN=4$ case suggests that there is an ``obvious'' one.
\owen{Feel free to reel back this overblown statement.}

We note that in the physics literature, there are a number of issues that are relevant in this setting.
For instance, there are ``instanton corrections'' that cannot be found by perturbative techniques, although they can be treated in a mathematically precise way. 
It is interesting to wonder how these would appear in the holomorphic setting.
